Stat 400 Project

### 2021-11-22 Stat 400 proj.Rmd
Make a more complete starting values function.

#create starting positions function
starting_vals <- function(num_subjects, x_dim, y_dim){

  start_x <- rep(NA, length(subjects))
  start_y <- rep(NA, length(subjects))

  for(i in 1:num_subjects){
  start_x[i] <- runif(n=1, min=0, max=grid_x)
  start_y[i] <- runif(n=1, min=0, max=grid_y)
  }

  return(cbind(start_x, start_y))
}

#simulation function
simulator <- function(days, num_subjects, x_dim, y_dim){
  subjects <- rep('S', num_subjects)
  start_coords <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim)
  starter_data <- cbind(subjects, start_coords)

>>>>

#create starting positions and state function
starting_vals <- function(num_subjects, I_0, x_dim, y_dim){

  #Storage for x, y starting positions for the subjects
  start_x <- rep(NA, num_subjects)
  start_y <- rep(NA, num_subjects)

  #Infect I_0 many starting subjects
  subjects <- rep('S', num_subjects)
  infect <- sample(x = 1:num_subjects, size=I_0, replace=FALSE)
  subjects[infect] <- 'I'

  #Assign starting positions randomly
  for(i in 1:num_subjects){
  start_x[i] <- runif(n=1, min=0, max=grid_x)
  start_y[i] <- runif(n=1, min=0, max=grid_y)
  }

  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  return(df)
}

#simulation function
simulator <- function(days, num_subjects, x_dim, y_dim, I_0){
  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
